\documentclass[10pt,a4paper]{article}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\author{Parker Whaley}
\title{PHYS 351 \#4}
\begin{document}
\maketitle

\section{Q1}
Recall that the van der Waals equation of state is $(P +\frac{a}{v^2} )(v - b) = RT$, where v is
the molar volume and a and b depend only on the type of gas.
\subsection{a}
The coefficient of thermal expansion is defined as follows:
\[\beta \equiv \frac{1}{V}(\frac{\partial V}{\partial T})\biggr |_P\]
Find $\beta$ for a van der Waals gas. Show that this reduces to the ideal gas result, $\beta_{ideal} =\frac{1}{T}$, when a = 0 and b = 0.\\

Lets start by taking a $\frac{\partial}{\partial T}$ holding P as a constant.  Noting that $v=V/n$ we begin taking a implicit derivative on boath sides.
\[\frac{\partial}{\partial T}(P +\frac{an^2}{V^2} )(V/n - b) = \frac{\partial}{\partial T}RT\]
\[(\frac{-2an^2}{V^3}\frac{\partial V}{\partial T}\biggr |_P )(V/n - b)+(P +\frac{an^2}{V^2} )(1/n\frac{\partial V}{\partial T}\biggr |_P) = R\]
\[\frac{\partial V}{\partial T}\biggr |_P =\frac{R}{(\frac{-2an^2}{V^3})(V/n - b)+(P +\frac{an^2}{V^2} )(1/n)}\]
\[\frac{\partial V}{\partial T}\biggr |_P =\frac{Rv^2V}{(-2a)(v - b)+(Pv^2 +a )(v)}=  \frac{Rv^2V}{2ab+(Pv^2-a)v}\]
\[\beta=\frac{Rv^2}{2ab-av+Pv^3}\]
(Cool $\beta$ is size independent, not dependent on V)  If we take the ideal gass limit (a=0 b=0) we get:
\[\beta=\frac{R}{Pv}\]
Noting that Pv=RT we see imeadiately:
\[\beta=\frac{1}{T}\]
Verifing the expected value for an ideal gas.
\subsection{b}
The coefficient of compression is defined as follows:
\[\kappa \equiv -\frac{1}{V}(\frac{\partial V}{\partial P})\biggr |_T\]
Find $\kappa$ for a van der Waals gas. Show that this reduces to the ideal gas result, $\kappa_{ideal} =\frac{1}{P}$, when $a = 0$ and $b = 0$.\\

Lets start by taking a $\frac{\partial}{\partial P}$ holding T as a constant.  Noting that $v=V/n$ we begin taking a implicit derivative on boath sides.
\[\frac{\partial}{\partial P}(P +\frac{an^2}{V^2} )(V/n - b) = \frac{\partial}{\partial P}RT\]
\[(1 +\frac{-2an^2}{V^3}\frac{\partial V}{\partial P}\biggr |_T )(V/n - b) + (P +\frac{an^2}{V^2} )(1/n\frac{\partial V}{\partial P}\biggr |_T) = 0\]
\[(1 +\frac{2a}{v^2}\kappa )(v - b) - (P +\frac{a}{v^2} )(v\kappa) = 0\]
\[2a\kappa (v - b) - (Pv^2 +a )(v\kappa) = (b - v)v^2\]
\[\kappa = \frac{(v - b)v^2}{ 2ab + Pv^3 -av }\]

This term is also size independent.  We note that as a and b become 0 the above becomes $\kappa_{ideal} =\frac{1}{P}$.
\section{Q2}
We have an elastic band. The Young’s modulus $Y$ is defined by the linear relation
between a differential change in length, $dL$, that results from the application of a
differential increment of force, $dF$: $dF =\frac{YA}{L_\circ}dL$, where the length is $L_\circ$ when no
force is applied, and the cross-sectional area is A.
\subsection{a}
Let the tension on the band be increased quasi-statically from $T_1$ to $T_2$. Calculate
the work done on the band, assuming that the cross-section does not change
appreciably.\\







\end{document}
